High-Dimensional Regularized Discriminant Analysis

### 2016-01-30 reports/paper-hdrda.Rnw
Rm'd a slight redundancy

In this section we compare the competing classifiers using the simulation design
from \cite{Guo:2007te}. This design is widely used within the high-dimensional
classification literature, including the studies by \cite{Ramey:2013ji} and
\cite{Witten:2011kc}. First, we consider the block-diagonal covariance matrix
from \cite{Guo:2007te},
\begin{align}
  \bm\Sigma_k = \bm\Sigma^{(\rho_k)} \oplus \bm\Sigma^{(-\rho_k)} \oplus \ldots \oplus \bm\Sigma^{(\rho_k)},\label{eq:block-sigma}
\end{align}
where the $(i,j)$th entry of the block matrix $\bm\Sigma^{(\rho_k)} \in
\mathbb{R}_{100 \times 100}$ is
\begin{align*}
\bm\Sigma_{ij}^{(\rho_k)} = \{ \rho_k^{|i - j|} \}_{1 \le i,j \le 100}.
\end{align*}
The block-diagonal covariance structure in \eqref{eq:block-sigma} resembles
gene-expression data: within each block of pathways, genes are correlated, and
the correlation decays as a function of the distance between any two genes. The
original design from \cite{Guo:2007te} comprised two $p$-dimensional
multivariate normal populations with a common block-diagonal covariance matrix
where $\bm\Sigma_1 = \bm\Sigma_2$.

>>>>

In this section we compare the competing classifiers using the simulation design
from \cite{Guo:2007te}. This design is widely used within the high-dimensional
classification literature, including the studies by \cite{Ramey:2013ji} and
\cite{Witten:2011kc}. First, we consider the block-diagonal covariance matrix
from \cite{Guo:2007te},
\begin{align}
  \bm\Sigma_k = \bm\Sigma^{(\rho_k)} \oplus \bm\Sigma^{(-\rho_k)} \oplus \ldots \oplus \bm\Sigma^{(\rho_k)},\label{eq:block-sigma}
\end{align}
where the $(i,j)$th entry of the block matrix $\bm\Sigma^{(\rho_k)} \in
\mathbb{R}_{100 \times 100}$ is
\begin{align*}
\bm\Sigma_{ij}^{(\rho_k)} = \{ \rho_k^{|i - j|} \}_{1 \le i,j \le 100}.
\end{align*}
The block-diagonal covariance structure in \eqref{eq:block-sigma} resembles
gene-expression data: within each block of pathways, genes are correlated, and
the correlation decays as a function of the distance between any two genes. The
original design from \cite{Guo:2007te} comprised two $p$-dimensional
multivariate normal populations with a common block-diagonal covariance matrix.
